An Investigation of Confusing Code Patterns in JavaScript

### 2023-01-11 s04.tex
Added file response_reviewer_1_2nd_round.md that addresses all the comments made by reviewer 1. I have also changed the order of the studies and made the appropriate adaptations for the MSR study to appear first, before the others and as a motivation for them.

To understand how often the analyzed atom candidates appear in open source JavaScript projects, and thus answer our third research question (\emph{What is the frequency of occurrence of atoms of confusion in practice?}), we mine a set of GitHub open source repositories and compute the prevalence of atom candidates.

\subsection{Study Settings}

@@

After filtering out JavaScript project candidates, we build a curated dataset comprising the top \minedprojects repositories. Examples of projects in this dataset include \textsc{React}, \textsc{Node JS}, and \textsc{AngularJS}. Table~\ref{tab:projects-statistics} presents some statistics about the projects we consider in our research. The size of the projects range from small ones (5543 lines of code) to complex systems with more than 1 MLOC. All projects in our dataset have at least \num{1244} forks and at least \num{23672} stars. We automate all the steps to filter, clone, and collect the statistics from the repositories using Python scripts.

@@

\begin{table}[ht]
  \centering
   \caption{Some descriptive statistics about the projects used in the MSR study}
%  \begin{scriptsize}
 \begin{tabular}{rrrrr}
   \toprule
                       & Min.             & Median        & Mean             & Max. \\ \midrule
 Lines of Code         & \num{5543}       & \num{36161.5} & \num{111432.33}  & \num{1278405} \\
 Num. of Forks         & \num{1244}       & \num{6078}    & \num{8906.24}    & \num{68849} \\
 Num. of Contributors  & \num{6}          & \num{285.5}   & \num{533.44}     & \num{4047} \\
 Num. of Stars         & \num{23672}      & \num{34990}   & \num{46919.51}   & \num{310935} \\

@@

Considering all JavaScript projects in our dataset, we found a total of \num{364873} atom candidates, though four atoms are responsible
for 92.97\% of this total: Implicit Predicate, Post Increment, Conditional Operator, and Omitted Curly Braces. The first two, based on the results of Section~\ref{sec:repeated} and Section~\ref{sec:latin}, can be considered atoms of confusion. The remaining atom
candidates comprise \num{25621} occurrences combined, 7.03\% of the total number of occurrences.
The Comma Operator and Arithmetic as Logic atoms are the ones that arise less
frequently (0.001\% in total with 232 and 165 occurrences, respectively).

% Regarding frequency, we proceeded with a classification of \emph{atom occurrence}
% based on thresholds used in a previous
% study~\cite{DBLP:journals/ese/MedeirosLAAKRG19}. 
% Atoms that occur 1000 times are classified as \textit{rarely used} while atoms with more than \num{10000} occurrences are classified as \textit{highly used}; \textit{commonly used} atoms occur in between.
We calculate the frequency of each atom per KLOC.
The four atoms mentioned in the previous paragraph,
Implicit Predicate, Post Increment, Conditional Operator, and Omitted Curly Braces, occur frequently in the analyzed projects. All of them have more than 5 occurrences per KLOC on average. In particular, two atom candidates occur very frequently, Implicit Predicate (19.89 occurrences per KLOC) and Conditional Operator (10.16 occurrences per KLOC). On the other hand, Arithmetic as Logic and Comma Operator occur less than once for every 50 KLOC.

@@

The results of our experiments and interviews suggest that Conditional Operator does not contribute significantly as a source of misunderstanding (increasing the number of wrong answers in 9\% of the cases, according to the Latin-square study). Nonetheless, the Post-Increment Expression and Automatic Semicolon Insertion atoms are listed in the top four sources of misunderstanding  (Table~\ref{tab:difference-correctness}), and also frequently appear in open source systems. As such, refactoring existing systems to avoid Post-Increment and Automatic Semicolon Insertion might improve the readability of large amounts of code in JavaScript projects.

>>>>

%To understand how often the analyzed atom candidates appear in open source JavaScript projects, and thus answer our third research question (\emph{What is the frequency of occurrence of atoms of confusion in practice?}), we mine a set of GitHub open source repositories and compute the prevalence of atom candidates.

We mine a set of GitHub open source repositories and compute how often these atom candidates occur. We do this with the goal of quantifying the prevalence of the investigated atom candidates. \revised{If they rarely occur in real-world systems, this would suggest that cannot be a significant source of confusion for developers. This study addresses our first research question (\emph{What is the frequency of occurrence of atom candidates in practice?}).}

\subsection{Study Setting}

@@

After filtering out JavaScript project candidates, we build a curated dataset comprising the top \minedprojects repositories. Examples of projects in this dataset include \textsc{React}, \textsc{Node JS}, and \textsc{AngularJS}. Table~\ref{tab:projects-statistics} presents some statistics about the projects we consider in our research. The size of the projects range from small ones (5543 lines of code) to complex systems with more than 1 MLOC. All projects in our dataset have at least \num[group-separator = {,}]{1244} forks and at least \num[group-separator = {,}]{23672} stars. We automate all the steps to filter, clone, and collect the statistics from the repositories using Python scripts.

@@

\begin{table}[ht]
  \centering
   \caption{Some descriptive statistics about the projects used in the MSR study}
%  \begin{scriptsize}
 \begin{tabular}{rrrrr}
   \toprule
                       & Min.             & Median        & Mean             & Max. \\ \midrule
 Lines of Code         & \num[group-separator = {,}]{5543}       & \num[group-separator = {,}]{36161.5} & \num[group-separator = {,}]{111432.33}  & \num[group-separator = {,}]{1278405} \\
 Num. of Forks         & \num[group-separator = {,}]{1244}       & \num[group-separator = {,}]{6078}    & \num[group-separator = {,}]{8906.24}    & \num[group-separator = {,}]{68849} \\
 Num. of Contributors  & \num[group-separator = {,}]{6}          & \num[group-separator = {,}]{285.5}   & \num[group-separator = {,}]{533.44}     & \num[group-separator = {,}]{4047} \\
 Num. of Stars         & \num[group-separator = {,}]{23672}      & \num[group-separator = {,}]{34990}   & \num[group-separator = {,}]{46919.51}   & \num[group-separator = {,}]{310935} \\

@@

Considering all JavaScript projects in our dataset, we found a total of \num[group-separator = {,}]{364873} atom candidates, though four atoms are responsible
for 92.97\% of this total: Implicit Predicate, Post Increment, Conditional Operator, and Omitted Curly Braces. 
%The first two, based on the results of Section~\ref{sec:repeated} and Section~\ref{sec:latin}, can be considered atoms of confusion. 
The remaining atom
candidates comprise \num[group-separator = {,}]{25621} occurrences combined, 7.03\% of the total number of occurrences.
The Comma Operator and Arithmetic as Logic atoms are the ones that arise less
frequently (0.001\% in total with 232 and 165 occurrences, respectively).

% Regarding frequency, we proceeded with a classification of \emph{atom occurrence}
% based on thresholds used in a previous
% study~\cite{DBLP:journals/ese/MedeirosLAAKRG19}. 
% Atoms that occur 1000 times are classified as \textit{rarely used} while atoms with more than \num[group-separator = {,}]{10000} occurrences are classified as \textit{highly used}; \textit{commonly used} atoms occur in between.
We calculate the frequency of each atom per KLOC.
The four atoms mentioned in the previous paragraph,
Implicit Predicate, Post Increment, Conditional Operator, and Omitted Curly Braces, occur frequently in the analyzed projects. All of them have more than 5 occurrences per KLOC on average. In particular, two atom candidates occur very frequently, Implicit Predicate (19.89 occurrences per KLOC) and Conditional Operator (10.16 occurrences per KLOC). On the other hand, Arithmetic as Logic and Comma Operator occur less than once for every 50 KLOC.

@@

%%%%%%%%%%%%%%%%%%%%%% MAYBE the following can go to a discussion section. 
%%%%%%%%%%%%%%%%%%%%%% 
%The first two, based on the results of Section~\ref{sec:repeated} and Section~\ref{sec:latin}, can be considered atoms of confusion.

%The results of our experiments and interviews suggest that Conditional Operator does not contribute significantly as a source of misunderstanding (increasing the number of wrong answers in 9\% of the cases, according to the Latin-square study). Nonetheless, the Post-Increment Expression and Automatic Semicolon Insertion atoms are listed in the top four sources of misunderstanding  (Table~\ref{tab:difference-correctness}), and also frequently appear in open source systems. As such, refactoring existing systems to avoid Post-Increment and Automatic Semicolon Insertion might improve the readability of large amounts of code in JavaScript projects.
